Reproducible, flexible and high throughput data extraction from primary literature: The \pkg{metaDigitise} \proglang{R} package \vskip15pt Supplementary Materials

### 2018-06-19 docs/MEE_submission/supplements.tex

\section{Comparison with existing software}
\begin{table}[h!]
\centering
\rotatebox{90}{%
\begin{minipage}{1.35\textwidth}
\small
\begin{tabular}{lccccccc}
\hline
Function                  & metaDigitise & GraphClick$^1$ & DataThief$^2$  & DigitizeIt$^3$ & WebPlotDigitizer$^4$ & metagear$^5$ & digitize$^6$\\
\hline
Scatterplots              & \checkmark   & \checkmark & \checkmark & \checkmark & \checkmark     & \checkmark$^7$ & \checkmark \\
Mean/error plots      & \checkmark   & \checkmark & \checkmark & $\times$   & $\times$       & \checkmark$^7$ & $\times$    \\
Boxplots                  & \checkmark   & $\times$   & $\times$   & $\times$   & $\times$       & $\times$       & $\times$    \\
Histograms                & \checkmark   & $\times$   & $\times$   & $\times$   & \checkmark$^7$ & $\times$       & $\times$    \\
Graph rotation$^8$        & \checkmark   & \checkmark & \checkmark & \checkmark & \checkmark     & $\times$       & $\times$    \\
Groups                    & \checkmark   & \checkmark & $\times$   & \checkmark & \checkmark     & $\times$       & $\times$    \\
Entry of metadata         & \checkmark   & $\times$   & $\times$   & $\times$   & $\times$       & $\times$       & $\times$    \\
Summarising data          & \checkmark   & $\times$   & $\times$   & $\times$   & $\times$       & $\times$       & $\times$    \\
Multiple image processing & \checkmark   & $\times$   & $\times$   & $\times$   & $\times$       & $\times$       & $\times$    \\
Reproducable$^9$  & \checkmark   & \checkmark & \checkmark & $\times$   & \checkmark     & $\times$       & $\times$    \\
Automated point detection & $\times$     & \checkmark &     $\times$      & \checkmark & \checkmark     & \checkmark     & $\times$    \\
Line extraction           & $\times$     & \checkmark & \checkmark & \checkmark & \checkmark     & $\times$       & $\times$    \\
Zoom                      & $\times$     & \checkmark & \checkmark & \checkmark & \checkmark     & $\times$       & $\times$    \\
Log axis                  & $\times$   & \checkmark & \checkmark & \checkmark & \checkmark     & $\times$       & $\times$    \\
Dates                     & $\times$   & $\times$   & \checkmark & $\times$   & \checkmark     & $\times$       & $\times$    \\
Asymmetric error bars     & $\times$     & $\times$   & \checkmark & $\times$   & $\times$       & $\times$       & $\times$    \\
Freeware                  & \checkmark$^{10}$ & \checkmark$^{11}$ & \checkmark$^{11}$ & $\times$$^{11}$ & \checkmark$^{11}$ & \checkmark$^{10}$ & \checkmark$^{10}$\\
\hline

>>>>

\section{Comparison with existing software}
\begin{table}[h!]
\centering
\rotatebox{90}{%
\begin{minipage}{1.35\textwidth}
\small
\begin{tabular}{lccccccc}
\hline
Function                  & metaDigitise & GraphClick$^1$ & DataThief$^2$  & DigitizeIt$^3$ & WebPlotDigitizer$^4$ & metagear$^5$ & digitize$^6$\\
\hline
Scatterplots              & \checkmark   & \checkmark & \checkmark & \checkmark & \checkmark     & \checkmark$^7$ & \checkmark \\
Mean/error plots      & \checkmark   & \checkmark & \checkmark & $\color{red}\times$   & $\color{red}\times$       & \checkmark$^7$ & $\color{red}\times$    \\
Boxplots                  & \checkmark   & $\color{red}\times$   & $\color{red}\times$   & $\color{red}\times$   & $\color{red}\times$       & $\color{red}\times$       & $\color{red}\times$    \\
Histograms                & \checkmark   & $\color{red}\times$   & $\color{red}\times$   & $\color{red}\times$   & \checkmark$^7$ & $\color{red}\times$       & $\color{red}\times$    \\
Graph rotation$^8$        & \checkmark   & \checkmark & \checkmark & \checkmark & \checkmark     & $\color{red}\times$       & $\color{red}\times$    \\
Groups                    & \checkmark   & \checkmark & $\color{red}\times$   & \checkmark & \checkmark     & $\color{red}\times$       & $\color{red}\times$    \\
Entry of metadata         & \checkmark   & $\color{red}\times$   & $\color{red}\times$   & $\color{red}\times$   & $\color{red}\times$       & $\color{red}\times$       & $\color{red}\times$    \\
Summarising data          & \checkmark   & $\color{red}\times$   & $\color{red}\times$   & $\color{red}\times$   & $\color{red}\times$       & $\color{red}\times$       & $\color{red}\times$    \\
Multiple image processing & \checkmark   & $\color{red}\times$   & $\color{red}\times$   & $\color{red}\times$   & $\color{red}\times$       & $\color{red}\times$       & $\color{red}\times$    \\
Reproducable$^9$  & \checkmark   & \checkmark & \checkmark & $\color{red}\times$   & \checkmark     & \checkmark       & $\color{red}\times$    \\
Automated point detection & $\color{red}\times$     & \checkmark &     $\color{red}\times$      & \checkmark & \checkmark     & \checkmark     & $\color{red}\times$    \\
Line extraction           & $\color{red}\times$     & \checkmark & \checkmark & \checkmark & \checkmark     & $\color{red}\times$       & $\color{red}\times$    \\
Zoom                      & $\color{red}\times$     & \checkmark & \checkmark & \checkmark & \checkmark     & $\color{red}\times$       & $\color{red}\times$    \\
Log axis                  & \checkmark   & \checkmark & \checkmark & \checkmark & \checkmark     & $\color{red}\times$       & $\color{red}\times$    \\
Dates                     & $\color{red}\times$   & $\color{red}\times$   & \checkmark & $\color{red}\times$   & \checkmark     & $\color{red}\times$       & $\color{red}\times$    \\
Asymmetric error bars     & $\color{red}\times$     & $\color{red}\times$   & \checkmark & $\color{red}\times$   & $\color{red}\times$       & $\color{red}\times$       & $\color{red}\times$    \\
Freeware                  & \checkmark$^{10}$ & \checkmark$^{11}$ & \checkmark$^{11}$ & $\color{red}\times$$^{11}$ & \checkmark$^{11}$ & \checkmark$^{10}$ & \checkmark$^{10}$\\
\hline
